VFTS682: a confirmed dynamical ejection?

### 2018-05-08 VFTS682.tex
downloaded new data, a bit more trustworthy

In \Secref{sec:sample}, we describe the data selection and validation
process for VFTS 682 and for stars in the surrounding used to
calculate and remove the mean motion of the
region. \Secref{sec:results} presents our main findings. We conclude
by discussing the implications for theories of
star formation, N-body interactions, and binary evolution in
\Secref{sec:discussion}.

@@

VFTS682 is labeled in the Gaia DR2
catalog\footnote{\url{https://gea.esac.esa.int/archive/}} with the
source id 4657685637907503744. The star has a
\texttt{visibility\_period} = 17, which counts how many observations have
been used to reconstruct its astrometric solution \citep[][]{lindengren:18}. Its G-band
magnitude is 15.65, cf. the V-band magnitude of 16.08
\citep[][]{evans:11, bestenlehner:11}, and the reported
\texttt{astrometric\_noise} = 0. These values suggest that the Gaia
data for VFTS682 are trustworthy. However, the effective temperature
reported is one order of magnitude lower than what found by
\cite{bestenlehner:11}, and the best fit parallax of this star is
negative. We do not use the effective temperature of the star anywhere
in this study, and we attribute the unphysical value of the parallax
to the large distance to the LMC. Our main findings do not rely on the
parallax value reported in the Gaia catalog.

@@

To compare the astrometry of VFTS682 and derive its peculiar motion,
we then select data from the Gaia DR2 catalog for two regions: the
``surroundings'' of VFTS 682, and the ``R136 cluster''. The
surrounding region is defined by all the stars within 10 arcminutes from
VFTS682 \todo{without a pm and with G mag<17 for VFTS completeness and
to focus on massive stars only}. This includes the subset of stars which we consider to be
part of R136. We include all the stars for which a value of the proper
motion components and the corresponding errors are available.
The ``R136 cluster'' is effectively defined by taking all the stars
within 25 arcseconds from R136a, one of the most massive members of
the cluster itself \citep[][]{crowther:10}. \todo{improve definition
  of stars from R136 -- check with Danny}

@@

The data retrieved, and the ipython notebook used for the analysis
presented here will be made available at \todo{probably git repo on bitbucket?}. 
\section{The kinematics of VFTS682}
\label{sec:results}

@@

\end{document}

>>>>

In \Secref{sec:sample}, we describe the data selection and validation
process for VFTS 682 and for stars in the surrounding used to
define the local reference frame. \Secref{sec:results} presents our main findings. We conclude
by discussing the implications for theories of
star formation, N-body interactions, and binary evolution in
\Secref{sec:discussion}.

@@

VFTS682 is labeled in the Gaia DR2
catalog\footnote{\url{https://gea.esac.esa.int/archive/}} with the
source id 4657685637907503744. The star has a
\texttt{visibility\_period} = 17, which counts how many observations have
been used to reconstruct its astrometric solution \citep[][]{lindengren:18}. Its G-band
magnitude is 15.65, cf. the V-band magnitude of 16.08
\citep[][]{evans:11, bestenlehner:11}, and the reported
\texttt{astrometric\_excess\_noise} = 0. These values suggest that the Gaia
data for VFTS682 are trustworthy. However, the effective temperature
reported is one order of magnitude lower than what found by
\cite{bestenlehner:11}, and the best fit parallax of this star is
negative. We do not use the effective temperature of the star anywhere
in this study, and we attribute the unphysical value of the parallax
to the large distance to the LMC. Our main findings do not rely on the
parallax value reported in the Gaia catalog.

@@

To compare the astrometry of VFTS682 and derive its peculiar motion,
we then select data from the Gaia DR2 catalog for two regions: the
``surroundings'' of VFTS 682, and the ``R136 cluster''. The
surrounding region is defined by all the stars in a target of 10 arcminutes around
VFTS682 fulfilling the following criteria: we require a G-band
magnitude brighter than 17, to mimic the completeness threshold for
the VFTS survey, \texttt{visibility\_period} >= 5, and
\texttt{astrometric\_excess\_noise} <= 1. This selection yields
roughly 17800 stars, including the subset of stars which we consider to be
part of R136, discussed below. We further require  these stars to have finite proper
motion components and relative errors, reducing further the sample to
14856 stars. % A more strict sample selection for the surroundings can
% be found in \cite{lennon:18}.

The ``R136 cluster'' is effectively defined by taking all the stars
within 25 arcseconds from R136a, one of the most massive members of
the cluster itself \citep[][]{crowther:10}, requiring the same
``quality'' criteria applied above. Because of the magnitude cut
however, this would yield an incredibly small sample of 15 stars only
% which makes no sense at all
\todo{improve definition
  of stars from R136, describe accordingly -- check with Danny}

@@

The data retrieved, and the ipython notebook used for the analysis
presented here will be made available at \todo{probably git repo on bitbucket?}.

\section{The kinematics of VFTS682}
\label{sec:results}

@@

% \begin{acknowledgements}
%  I am grateful to S.~Torres who helped me p
% \end{acknowledgements}
\end{document}
